Simulation_Study

### 2022-02-28 Simulation_Study.Rmd
Quantile Interval

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n, sd = sd)
  bt <- blkboot(x, statistic, 1000, l) 
  nm_interval = c(bt$stat - 1.96*sd(bt$nm.stat), bt$stat + 1.96*sd(bt$nm.stat))
  mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
  if (0.5 >)
  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval) 
    # returns statistics and sd's for nm and mv respectively

@@

Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1

```{r functions, echo = False}
ar1 <- function(x) cor(x[-1], x[-length(x)])
sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, ar1))
print(sim)

>>>>

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sd) 
  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

  # Variance Stuff that isn't working
  # 95 % Confidence Interval for Variance -> Lower bound: (n - 1) * sample_variance(X_t) / chisq(.025, n - 1)
  # Upper bound: (n - 1) * sample_variance(X_t) / chisq(.975, n - 1)
  # sample_variance(X_t) = se^2 * n

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  if (nm_interval[1] < 0 && nm_interval[2] > 0)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < 0 && mv_interval[2] > 0)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

@@

Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01)

```{r functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)
nmcount = 0
mvcount = 0
nmchicount = 0
mvchicount = 0

sim <- replicate(100, do1rep(100, 0.1, 0.1, 10, m1))

my_summary <- function(x)
{
  c(rowMeans(x), sd(x[1,]))
}
my_summary(sim)
print(sim)

#Counts how many times the true statistic was found in the interval
